### 2025-05-22 acknowledgments.tex
Minor changes

\section*{Acknowledgments}

@@

The author also want to thanks to her family for their unconditional love, belief in her, and emotional support, even from afar. Their presence—whether near or distant—gave her strength through every challenge.

To dear friend \emph{Le Manh Tai}, thank you for always being there—for every late night, every deadline, and every quiet moment of doubt. Your support made a difference more than words can say.

>>>>

\chapter*{Acknowledgments}
\label{ack}

@@

The author also wants to thanks to her family for their unconditional love, belief in her, and emotional support, even from afar. Their presence—whether near or distant—gave her strength through every challenge.

To her dear friend \emph{Le Manh Tai}, thank you for always being there—for every late night, every deadline, and every quiet moment of doubt. Your support made a difference more than words can say.
